Prospective testing for the prevalence or transience of a shock effect over a set time horizon before it occurs

### 2022-08-26 prevalence_testing/postshocktest2022draft.tex
addition with tables and comments

\begin{table}[H]
	\caption{Results for Month-on-Month Change in Log Nonfarm Payrolls (Seasonally Adjusted) ($n=3$), $\mbf{W}^* = (0.196, 0.804, 0.000)$ from scaled covariates}   \label{uemtable}
\begin{center}
  \begin{tabular}{cccccccccr}
     $H$  & Model &   $p_1$ & $\hat{p}_1$ & $|\hat{p}_1-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
     \hline 
     \multirow{2}{*}{2} & $\mc{M}_0$  &   0.300 & 0.443  & 0.143 & 0 (Yes) & 0 (Yes)\\      
      & $\mc{M}$  & 0.775 & 0.591 & $0.184$   & 0 (Yes) &0 (Yes)   \\[.2cm]
     \multirow{2}{*}{3} & $\mc{M}_0$ &   0.215 & 0.477 & $0.262$ & 0 (Yes) & 0 (Yes)    \\
      &  $\mc{M}$ & 0.740 & 0.600 & 0.140 & 0 (Yes) & 0 (Yes)  \\[.2cm]
     \multirow{2}{*}{4} &  $\mc{M}_0$ &   0.615   & $0.343$ & 0.272 & 0 (Yes) & 0 (Yes)  \\
      &  $\mc{M}$ & 0.780 & 0.464  & 0.316 & 0 (Yes) & 0 (Yes) \\[.2cm]
     \multirow{2}{*}{5} & $\mc{M}_0$ & 0.030 & 0.377 & 0.347 & 0 (No) & 0 (No)\\
     & $\mc{M}$ & 0.940 & 0.293 & 0.647 & 0 (Yes) & 0 (Yes)
  \end{tabular}
\end{center}	
\end{table}

@@

\vspace*{0.5cm}\textcolor{red}{A naive test for the presence of a mean-shift shock effect predictably decays very quickly as more and more post-shock data is added for fitting purposes when, in truth, the shock is transient. However, the Quaedvlieg method runs $h = 1,...,H$ ahead forecasts that will not necessarily indicate a quickly decaying shock due to the training data for the model including post-shock responses that have yet to decay. Thus the unadjusted and adjusted forecasts can deviate sharply when their underlying models are fit to a small amount of post-shock data. When $H$ is small, there is a lot of post-shock data under consideration, and the shock decays quickly, the initial shock   may not be detected by the Quaedvlieg method due to a loss-difference matrix evaluating several differences that are negligible far away from the initial shock. The same can be true when $H$ is large. However, for medium size $H$, the influence of fitting the initial post-shock data may not yet accommodate the sharply decayed shock. The result of this is that the Quaedvlieg method can indicate a shifted significant difference between the adjusted and un-adjusted forecasts.  (loss-difference matrix has dimensions $(T - T^* - \max(\lceil1.5\sqrt{T - T^*}\rceil, H))  \times H$) When we have limited sample size, we should not consider large $H$.}

>>>>

\begin{table}[H]
	\caption{Results for Month-on-Month Change in Log Nonfarm Payrolls for $\mc{M}_0$ (Seasonally Adjusted) ($n=3$), $\mbf{W}^* = (0.196, 0.804, 0.000)$ from scaled covariates}   \label{uemtable}
\begin{center}
  \begin{tabular}{cccccccccr}
     $H$   &   $p_1$ & $\hat{p}_1$ & $|\hat{p}_1-p_1|$ & Vote (Correct?) & weighted Vote (Correct?)   \\
     \hline 
 2   & 0.33 & 0.21 & 0.12 & 0 (Yes) & 0 (Yes) \\ 
   3   & 0.11 & 0.51 & 0.40 & 0 (Yes) & 0 (Yes) \\ 
   4   & 0.43 & 0.52 & 0.09 & 0 (Yes) & 0 (Yes) \\ 
   5   & 0.02 & 0.36 & 0.34 & 0 (No) & 0 (No) \\  
   6   & 0.04 & 0.62 & 0.58 & 0 (No) & 0 (No) \\ 
   7   & 0.03 & 0.40 & 0.37 & 0 (No) & 0 (No) \\ 
   8  & 0.27 & 0.46 & 0.19 & 0 (Yes) & 0 (Yes) \\ 
   9   & 0.49 & 0.27 & 0.22 & 0 (Yes) & 0 (Yes) \\ 
   10  & 0.76 & 0.67 & 0.10 & 0 (Yes) & 0 (Yes) \\ 
  \end{tabular}
\end{center}	
\end{table}

@@

\textcolor{red}{From Table \ref{uemtable}, $p_1$ is insignificant for $H = 2, 3, 4$ and $H = 8, 9, 10$ but is significant for $H = 5, 6, 7$. Notice that weighted voting, vote, and $\hat{p}_1$ also does not perform well for $H = 5, 6, 7$.  This implies something undetected and unique  to the time series of interest occur.  For this reason, we investigated the point estimates of the shock effects using data from $t = T_1^*+r-37$ to $t = T_1^* + r$.  Note that for different $r$, the training sample size is fixed and thus prevents training sample size to affect inference results. The results are presented in Table \ref{pesr} with point estimates of the shock effects denoted by $\hat{\alpha}_{1, r}$ and corresponding standard error and $p$-value from $t$-test. Note that the $t$-test is significant for $r = 1, 2, 3, 4$ but insignificant for $r\geq 5$.}

\vspace*{0.5cm}\textcolor{red}{ This naive test implies that  the presence of a mean-shift shock effect predictably decays very quickly as more and more post-shock data is added for fitting purposes when, in truth, the shock is transient. However, the Quaedvlieg method runs $h = 1,...,H$ ahead forecasts that will not necessarily indicate a quickly decaying shock due to the training data for the model including post-shock responses that have yet to decay. Thus the unadjusted and adjusted forecasts can deviate sharply when their underlying models are fit to a small amount of post-shock data. When $H$ is small, there is a lot of post-shock data under consideration, and the shock decays quickly, the initial shock   may not be detected by the Quaedvlieg method due to a loss-difference matrix evaluating several differences that are negligible far away from the initial shock. The same can be true when $H$ is large. However, for medium size $H$, the influence of fitting the initial post-shock data may not yet accommodate the sharply decayed shock. The result of this is that the Quaedvlieg method can indicate a shifted significant difference between the adjusted and un-adjusted forecasts.  (loss-difference matrix has dimensions $(T - T^* - \max(\lceil1.5\sqrt{T - T^*}\rceil, H))  \times H$) When we have limited sample size, we should not consider large $H$.}

\begin{table}[H]
	\caption{Point estimates of shock effects under $\mc{M}_0$ using data from $t = T_1^* + r-37$ to $T^*_1 + r$} \label{pesr}
	\begin{center}
		\begin{tabular}{rrcr} 
 $r$& $\hat{\alpha}_{1,r}$ & $\sqrt{\hat{\mathbf{Var}}(\hat{\alpha}_{1,r})}$ & $p$-value \\ 
  \hline
 1 & $-$0.1344 & 0.0134 & 0.0000 \\ 
  2 & $-$0.1379 & 0.0138 & 0.0000 \\ 
  3 & $-$0.1921 & 0.0469 & 0.0002 \\ 
  4 & $-$0.0055 & 0.0065 & 0.4056 \\ 
  5 & 0.0054 & 0.0041 & 0.1950 \\ 
  6 & $-$0.0013 & 0.0025 & 0.6213 \\ 
  7 & $-$0.0042 & 0.0025 & 0.1003 \\ 
  8 & $-$0.0028 & 0.0022 & 0.2109 \\ 
  9 & $-$0.0010 & 0.0020 & 0.6203 \\ 
  10 & 0.0005 & 0.0019 & 0.7788 \\ 
  11 & 0.0006 & 0.0018 & 0.7636 \\ 
  12 & 0.0029 & 0.0019 & 0.1368 \\ 
  13 & 0.0024 & 0.0022 & 0.2823 \\ 
  14 & 0.0025 & 0.0021 & 0.2442 \\ 
  15 & 0.0015 & 0.0021 & 0.4883 \\ 
  16 & 0.0008 & 0.0023 & 0.7245 \\ 
  17 & 0.0013 & 0.0022 & 0.5693 \\ 
  18 & 0.0015 & 0.0022 & 0.4907 \\ 
   \hline
\end{tabular}
	\end{center}	
\end{table}
